Biometry / Homework 2 / Auriel Fournier / March 8, 2014
========================================================

```{r, warning=FALSE, message=FALSE}
setwd("C:/Users/avanderlaar/Dropbox/R/Biometry_HW_2")

library(lattice)
library(ggplot2)
library(sciplot)
library(psych)
library(sjPlot)
library(pwr)
library(compute.es)
```

I've take the data I was given for this assignment and saved it as a .csv file.
```{r}
fish <- read.csv('Biometry_HW_2.csv', header=TRUE)
```

The head() command shows the first 6 rows of each column
```{r}
head(fish)
```

make sure that all the variables were imported as the right kind of data

```{r}
str(fish)
```

look at the very basic stats of each variable

```{r}
summary(fish)
```

This provides summary stats by group

SEASON
```{r}
describeBy(fish$TOTDENVOL, group=fish$SEASNUM)
```
Stream Type
```{r}
describeBy(fish$TOTDENVOL, group=fish$STREAMTYPE)
```

Graphical Examination
========================================================
Box Plots
---------------------------------------------------------
```{r}
plot(fish$TOTDENVOL ~ as.factor(fish$SEASNUM), ylab="Fish Density", xlab="Season")
```
### Figure 1 - Fish Density by Season

```{r, warning=FALSE, message=FALSE}
png(filename="seasonbox.png")
plot(fish$TOTDENVOL ~ as.factor(fish$SEASNUM), ylab="Fish Density", xlab="Season")
dev.off()
```

```{r}
plot(fish$TOTDENVOL ~ as.factor(fish$STREAMTYPE), ylab="Fish Density", xlab="Stream Type")
```
### Figure 2 - Fish Density by Stream Type

```{r}
png(filename="streambox.png")
plot(fish$TOTDENVOL ~ as.factor(fish$STREAMTYPE), ylab="Fish Density", xlab="Stream Type")
dev.off()
```
Histograms
-------------------------------------------------------------------

```{r}
histogram(~TOTDENVOL|SEASNUM, fish, xlab="Fish Density") 
```
### Figure 3 - Distribution of Fish Density by Season
```{r}
png(filename="seasonhist.png")
histogram(~TOTDENVOL|SEASNUM, fish, xlab="Fish Density") 
dev.off()
```

```{r}
histogram(~TOTDENVOL|STREAMTYPE, fish, xlab="Fish Density")
```
### Figure 4 - Distribution of Fish Density by Stream Type
```{r}
png(filename="streamhist.png")
histogram(~TOTDENVOL|STREAMTYPE, fish, xlab="Fish Density")
dev.off()
```
Square-root Transformation
------------------------------------------

```{r}
fish[,71] = sqrt(fish$TOTDENVOL)
```
Bar Plots
---------------
```{r}
plot(fish$V71 ~ as.factor(fish$SEASNUM), ylab="Fish Density", xlab="Season")
```
### Figure 5 - Square Root Transformed Fish Density by Season
```{r}
png(filename="squareboxseason.png")
plot(fish$V71 ~ as.factor(fish$SEASNUM), ylab="Fish Density", xlab="Season")
dev.off()
```
```{r}
plot(fish$V71 ~ as.factor(fish$STREAMTYPE), ylab="Fish Density", xlab="Stream Type")
```
### Figure 6 - Square Root Transformed Fish Density by Stream Type
```{r}
png(filename="squareboxstream.png")
plot(fish$V71 ~ as.factor(fish$STREAMTYPE), ylab="Fish Density", xlab="Stream Type")
dev.off()
```
Histograms
-----------------
```{r}
histogram(~V71|SEASNUM, fish, xlab="Fish Density") 
```
### Figure 7 - Distribution of Square Root Transformed Fish Density by Season
```{r}
png(filename="squareseasonhist.png")
histogram(~V71|SEASNUM, fish, xlab="Fish Density") 
dev.off()
```
```{r}
histogram(~V71|STREAMTYPE, fish, xlab="Fish Density")
```
### Figure 8 - Distribution of Square Root Transformed Fish Density by Stream Type
```{r}
png(filename="squarestreamhist.png")
histogram(~V71|STREAMTYPE, fish, xlab="Fish Density")
dev.off()
```
4th-root transformation
------------------------

```{r}

fish[,72] = fish$V71^(1/4)
```
Bar Plot
--------------------
```{r}
plot(fish$V72 ~ as.factor(fish$SEASNUM), ylab="Fish Density", xlab="Season")
```
### Figure 9 - Fourth Root Transformed Fish Density by Season
```{r}
png(filename="fourboxseason.png")
plot(fish$V72 ~ as.factor(fish$SEASNUM), ylab="Fish Density", xlab="Season")
dev.off()
```

```{r}
plot(fish$V72 ~ as.factor(fish$STREAMTYPE), ylab="Fish Density", xlab="Stream Type")
```
### Figure 10 -Fourth Root Transformed Fish Density by Stream Type
```{r}
png(filename="fourboxstream.png")
plot(fish$V72 ~ as.factor(fish$STREAMTYPE), ylab="Fish Density", xlab="Stream Type")
dev.off()
```
Histogram
------------------
```{r}
histogram(~V72|SEASNUM, fish, xlab="Fish Density") 
```
### Figure 11 - Distribution of Fourth Root Transformed Fish Density by Season
```{r}
png(filename="fourhistseason.png")
histogram(~V72|SEASNUM, fish, xlab="Fish Density")
dev.off()
```

```{r}
histogram(~V72|STREAMTYPE, fish, xlab="Fish Density")
```
### Figure 12 - Distribution of Fourth Root Transformed Fish Density by Season
```{r}
png(filename="fourhiststream.png")
histogram(~V72|STREAMTYPE, fish, xlab="Fish Density")
dev.off()

```

Two-Way ANOVA on Season and Stream Type
========================================================

```{r}
model <- lm(V72 ~  STREAMTYPE * SEASNUM, data=fish)
anova_two <- anova(model)
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(model)
```
### Figure 13 - Two-Way Anova Output Graphs
```{r}
png(filename="TwoANOVA.png")
layout(matrix(c(1,2,3,4),2,2))
plot(model)
dev.off()
```

Code to Generate Table
```{r}
#sjt.df(anova_two, alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr
```

### Table 1 - Two Way ANOVA on Stream Type and Season 

`r sjt.df(anova_two, alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`

Residual Plot
-------------------
```{r}
fish.df <- data.frame(M1_Fit = seq(0,0, length=150), 
                      M1_Resid = seq(0,0, length=150),
                      Season = seq(0,0, length=150),
                      Stream = seq(0,0, length=150))
                      
fish.resid = resid(model)
fish.fitted = fitted(model)

fish.df$M1_Fit = fish.fitted
fish.df$M1_Resid = fish.resid
fish.df$Season = fish$SEASNUM  
fish.df$Stream = fish$STREAMNUM

ggplot(fish.df, aes(M1_Fit, M1_Resid, colour =Stream)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of Two-way Anova")
```
### Figure 14 - Residual Plot from Two Way ANOVA on Stream Type and Season 
```{r}
png(filename="TwoANOVAResidual.png")
ggplot(fish.df, aes(M1_Fit, M1_Resid, colour =Stream)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of Two-way Anova")
dev.off()
```

Interaction Plot
-------------------------
```{r}

lineplot.CI(SEASNUM,V72, group =STREAMTYPE , data =fish, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            col = c("blue","red"), pch = c(16,16))
```
### Figure 15 - Interaction Plot of Stream Type and Season from Two Way Anova
```{r}
png(filename="TwoANOVAInteraction.png")
lineplot.CI(SEASNUM,V72, group =STREAMTYPE , data =fish, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            col = c("blue","red"), pch = c(16,16))
dev.off()


```

One-Way ANOVA On Stream Type
========================================================

```{r}
stream <- lm(V72 ~  STREAMTYPE, data=fish) 

```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(stream)
```
### Figure 16 - ANOVA Output Plots for One Way Anova on Stream Type
```{r}
png(filename="OneANOVAStream.png")
layout(matrix(c(1,2,3,4),2,2))
plot(stream)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(stream), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 2 - One Way Anova on Stream Type

`r sjt.df(anova(stream), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`

Residual Plot
--------------------
```{r}
stream.df <- data.frame(M1_Fit = seq(0,0, length=150), 
                      M1_Resid = seq(0,0, length=150),
                      Stream = seq(0,0, length=150))

stream.resid = resid(stream)
stream.fitted = fitted(stream)

stream.df$M1_Fit = stream.fitted
stream.df$M1_Resid = stream.resid
stream.df$Stream = fish$STREAMNUM

ggplot(stream.df, aes(M1_Fit, M1_Resid, colour =Stream)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Stream Type")
```
### Figure 17 - Residuals from One Way Anova on STream Type
```{r}
png(filename="OneANOVAStreamResidual.png")
ggplot(stream.df, aes(M1_Fit, M1_Resid, colour =Stream)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Stream Type")
dev.off()

```

Interaction Plot
-----------------
```{r}
lineplot.CI(STREAMTYPE,V72, data =fish, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
             pch = c(16,16))
```
### Figure 18 - Interaction Plot from One Way Anova on Stream Type
```{r}
png(filename="OneANOVAStreamInteraction.png")
lineplot.CI(STREAMTYPE,V72, data =fish, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
             pch = c(16,16))
dev.off()

```

One-Way ANOVA On Season With Tukey's Test
========================================================

Now lets look at a One-way ANOVA on season

```{r}
season <- lm(V72 ~  SEASNUM, data=fish) 
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(season)
```
### Figure 19 - Output Graphs from One way Anova on Season
```{r}
png(filename="OneANOVA.png")
layout(matrix(c(1,2,3,4),2,2))
plot(season)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(season), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 3 - One Way Anova on Season

`r sjt.df(anova(season), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`
Residual Plot
-----------------
```{r}
season.df <- data.frame(M1_Fit = seq(0,0, length=150), 
                        M1_Resid = seq(0,0, length=150),
                        Season = seq(0,0, length=150))

season.resid = resid(season)
season.fitted = fitted(season)

season.df$M1_Fit = season.fitted
season.df$M1_Resid = season.resid
season.df$Season = fish$SEASNUM

ggplot(season.df, aes(M1_Fit, M1_Resid, colour =Season)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")
```
### Figure 20 - Residuals from One Way Anova on Season
```{r}
png(filename="OneANOVASeasonResidual.png")
ggplot(season.df, aes(M1_Fit, M1_Resid, colour =Season)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")

dev.off()


```


Interaction Plot
-------------------
```{r}
lineplot.CI(SEASNUM,V72, data =fish, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
```
### Figure 21 - Interaction Plot fron One Way Anova on Season
```{r}
png(filename="OneANOVASeasonInteraction.png")
lineplot.CI(SEASNUM,V72, data =fish, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
dev.off()

```


```{r}
fish[,3] = factor(fish$SEASNUM)

seasonanova <- aov(fish$V72 ~ fish$SEASNUM)
TukSeason = TukeyHSD(x=seasonanova, conf.level=0.95)
```
###Table 4 - Tukey Test Output Table for ONe Way Anova on Season
```{r}
TukSeason
```

One Way Anova on Season for Boston Mountains With Tukey's Test
========================================================

```{r}
Boston = fish[fish$STREAMTYPE=='1',]

boston <- lm(V72 ~  SEASNUM, data=Boston) 
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(boston)
```
### Figure 22 - Outplut Graphs for One Way Anova on Season in Boston Mountains
```{r}
png(filename="OneANOVABoston.png")
layout(matrix(c(1,2,3,4),2,2))
plot(boston)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(boston), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 5 - One Way ANOVA on Season in Boston Mountains

`r sjt.df(anova(boston), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`
Residual Plot
-----------------
```{r}
boston.df <- data.frame(M1_Fit = seq(0,0, length=73), 
                        M1_Resid = seq(0,0, length=73),
                        Season = seq(0,0, length=73))

boston.resid = resid(boston)
boston.fitted = fitted(boston)

boston.df$M1_Fit = boston.fitted
boston.df$M1_Resid = boston.resid
boston.df$Season = Boston$SEASNUM

ggplot(boston.df, aes(M1_Fit, M1_Resid, colour =Season)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")
```
### Figure 23 - Residuals from One Way Anova on Season in Boston Mountains
```{r}
png(filename="OneANOVASeasonResidualBoston.png")
ggplot(boston.df, aes(M1_Fit, M1_Resid, colour =Season)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")

dev.off()


```


Interaction Plot
-------------------
```{r}
lineplot.CI(SEASNUM,V72, data =Boston, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
```
### Figure 24 - Interaction Plot of One Way ANOVA on Season in Boston Mountains
```{r}
png(filename="OneANOVASeasonInteractionBoston.png")
lineplot.CI(SEASNUM,V72, data =Boston, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
dev.off()

```

```{r}
Boston[,3] = factor(Boston$SEASNUM)

bostonanova <- aov(Boston$V72 ~ Boston$SEASNUM)
TukBoston = TukeyHSD(x=bostonanova, conf.level=0.95)
```
###Table 6 - Tukey Test from One Way Anova on Season in Boston Mountains
```{r}
TukBoston
```

One Way Anova on Season for Ozark Highlands with Tukey's Test
========================================================

```{r}
Ozark = fish[fish$STREAMTYPE=='2',]

ozark <- lm(V72 ~  SEASNUM, data=Ozark) 
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(ozark)
```
### Figure 25 - Output Graphs from One Way ANOVA on Season in Ozarks
```{r}
png(filename="OneANOVAOzark.png")
layout(matrix(c(1,2,3,4),2,2))
plot(ozark)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(ozark), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 7 - Output from One Way ANOVA on Season in Ozarks

`r sjt.df(anova(ozark), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`
Residual Plot
-----------------
```{r}
ozark.df <- data.frame(M1_Fit = seq(0,0, length=77), 
                        M1_Resid = seq(0,0, length=77),
                        Season = seq(0,0, length=77))

ozark.resid = resid(ozark)
ozark.fitted = fitted(ozark)

ozark.df$M1_Fit = ozark.fitted
ozark.df$M1_Resid = ozark.resid
ozark.df$Season = Ozark$SEASNUM

ggplot(ozark.df, aes(M1_Fit, M1_Resid, colour =Season)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")
```
### Figure 26 - Residuals from One Way ANOVA on Season in Ozarks
```{r}
png(filename="OneANOVASeasonResidualOzark.png")
ggplot(ozark.df, aes(M1_Fit, M1_Resid, colour =Season)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")

dev.off()


```


Interaction Plot
-------------------
```{r}
lineplot.CI(SEASNUM,V72, data =Ozark, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
```
### Figure 27 - Interaction Plot from One Way ANOVA on Season in Ozarks
```{r}
png(filename="OneANOVASeasonInteractionOzark.png")
lineplot.CI(SEASNUM,V72, data =Ozark, cex = 1.5,
            xlab = "Season", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
dev.off()

```


```{r}
Ozark[,3] = factor(Ozark$SEASNUM)

ozarkanova <- aov(Ozark$V72 ~ Ozark$SEASNUM)
TukOzark = TukeyHSD(x=ozarkanova, conf.level=0.95)
```
###Table 8 - Tukey Test Output from One Way ANOVA on Season in Ozarks
```{r}
TukOzark
```

One Way Anova on Stream Type for Spring
========================================================


```{r}
Spring = fish[fish$SEASNUM=='4',]

spring <- lm(V72 ~  STREAMTYPE, data=Spring) 
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(spring)
```
### Figure 28 - Output Graphs from One Way ANOVA on Stream Type during Spring
```{r}
png(filename="OneANOVASpring.png")
layout(matrix(c(1,2,3,4),2,2))
plot(spring)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(spring), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 9 - Results of One Way ANOVA on Stream Type during Spring

`r sjt.df(anova(spring), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`
Residual Plot
-----------------
```{r}
spring.df <- data.frame(M1_Fit = seq(0,0, length=36), 
                        M1_Resid = seq(0,0, length=36),
                        Season = seq(0,0, length=36))

spring.resid = resid(spring)
spring.fitted = fitted(spring)

spring.df$M1_Fit = spring.fitted
spring.df$M1_Resid = spring.resid
spring.df$StreamType = Spring$STREAMTYPE

ggplot(spring.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")
```
### Figure 29 - Interaction Plot from One Way ANOVA on Stream Type during Spring
```{r}
png(filename="OneANOVASeasonResidualSpring.png")
ggplot(spring.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")

dev.off()


```


Interaction Plot
-------------------
```{r}
lineplot.CI(STREAMTYPE,V72, data =Spring, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
```
### Figure 30 - Interaction Plot from One Way ANOVA on Stream Type during Spring
```{r}
png(filename="OneANOVASeasonInteractionSpring.png")
lineplot.CI(STREAMTYPE,V72, data =Spring, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
dev.off()

```

One Way Anova on Stream Type for Early Summer
========================================================


```{r}
Early = fish[fish$SEASNUM=='6',]

early <- lm(V72 ~  STREAMTYPE, data=Early) 
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(early)
```
### Figure 31 - Output graphs from One Way ANOVA on Stream Type during Early Summer
```{r}
png(filename="OneANOVAEarly.png")
layout(matrix(c(1,2,3,4),2,2))
plot(early)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(early), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 10 - Output from One Way ANOVA on Stream Type during Early Summer

`r sjt.df(anova(early), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`
Residual Plot
-----------------
```{r}
early.df <- data.frame(M1_Fit = seq(0,0, length=41), 
                        M1_Resid = seq(0,0, length=41),
                        Season = seq(0,0, length=41))

early.resid = resid(early)
early.fitted = fitted(early)

early.df$M1_Fit = early.fitted
early.df$M1_Resid = early.resid
early.df$StreamType = Early$STREAMTYPE

ggplot(early.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")
```
### Figure 32 - Residual Plot from One Way ANOVA on Stream Type during Early Summer
```{r}
png(filename="OneANOVASeasonResidualEarly.png")
ggplot(early.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")

dev.off()


```


Interaction Plot
-------------------
```{r}
lineplot.CI(STREAMTYPE,V72, data =Early, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
```
### Figure 33 - Interaction Plot from One Way ANOVA on Stream Type during Early Summer
```{r}
png(filename="OneANOVASeasonInteractionEarly.png")
lineplot.CI(STREAMTYPE,V72, data =Early, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
dev.off()

```

One Way Anova on Stream Type for Late Summer
========================================================

```{r}
Late = fish[fish$SEASNUM=='8',]

late <- lm(V72 ~  STREAMTYPE, data=Late) 
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(late)
```
### Figure 34 - Output Graphs from One Way ANOVA on Stream Type in Late Summer
```{r}
png(filename="OneANOVALate.png")
layout(matrix(c(1,2,3,4),2,2))
plot(late)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(late), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 11 - Output from One Way ANOVA on Stream Type in Late Summer

`r sjt.df(anova(late), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`
Residual Plot
-----------------
```{r}
late.df <- data.frame(M1_Fit = seq(0,0, length=38), 
                        M1_Resid = seq(0,0, length=38),
                        Season = seq(0,0, length=38))

late.resid = resid(late)
late.fitted = fitted(late)

late.df$M1_Fit = late.fitted
late.df$M1_Resid = late.resid
late.df$StreamType = Late$STREAMTYPE

ggplot(late.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")
```
### Figure 35 - Residuals Plot from One Way ANOVA on Stream Type in Late Summer
```{r}
png(filename="OneANOVASeasonResidualLate.png")
ggplot(late.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")

dev.off()


```


Interaction Plot
-------------------
```{r}
lineplot.CI(STREAMTYPE,V72, data =Late, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
```
### Figure 36 - Interaction Plot from One Way ANOVA on Stream Type in Late Summer
```{r}
png(filename="OneANOVASeasonInteractionLate.png")
lineplot.CI(STREAMTYPE,V72, data =Late, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
dev.off()

```

One Way Anova on Stream Type for Fall
========================================================


```{r}
Fall = fish[fish$SEASNUM=='10',]

fall <- lm(V72 ~  STREAMTYPE, data=Fall) 
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(fall)
```
### Figure 37 - Output graphs from One Way Anova on Stream Type during the Fall
```{r}
png(filename="OneANOVAFall.png")
layout(matrix(c(1,2,3,4),2,2))
plot(fall)
dev.off()
```

Code to generate table
```{r}
#sjt.df(anova(fall), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr

```
### Table 12 - Results of One Way ANOVA on Stream Type during the Fall

`r sjt.df(anova(fall), alternateRowColors=TRUE,  no.output=TRUE, describe=FALSE)$knitr`
Residual Plot
-----------------
```{r}
fall.df <- data.frame(M1_Fit = seq(0,0, length=35), 
                        M1_Resid = seq(0,0, length=35),
                        StreamType = seq(0,0, length=35))

fall.resid = resid(fall)
fall.fitted = fitted(fall)

fall.df$M1_Fit = fall.fitted
fall.df$M1_Resid = fall.resid
fall.df$StreamType = Fall$STREAMTYPE

ggplot(fall.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")
```
### Figure 38 - Residuals from One Way ANOVA on Stream Type during the Fall
```{r}
png(filename="OneANOVASeasonResidualFall.png")
ggplot(fall.df, aes(M1_Fit, M1_Resid, colour =StreamType)) + geom_point() +
  xlab("Fitted Values") + ylab("Residuals") + ggtitle("Residuals of One-Way Anova on Season")

dev.off()


```


Interaction Plot
-------------------
```{r}
lineplot.CI(STREAMTYPE,V72, data =Fall, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
```
### Figure 39 - Interaction Plot on One Way Anova on Stream Type during the Fall
```{r}
png(filename="OneANOVASeasonInteractionFall.png")
lineplot.CI(STREAMTYPE,V72, data =Fall, cex = 1.5,
            xlab = "Stream Type", ylab = "means", cex.lab = 1.2, x.leg = 1,
            pch = c(16,16))
dev.off()

```
